Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
Fewer short-period companions

@@

\subsection{Impossible companions}

@@

Tables available online, full code open source.\footnote{The code used in this
project is available from \url{https://github.com/adrn/TwoFace} under the MIT
open-source software license.}

>>>>

Red clump (\RC) stars are horizontal branch stars and have therefore already
climbed the RGB, where the surface of the star can grow to be several AU in
size.
\RC\ stars are therefore expected to less frequently have companions at short
periods ($P<XX$~day) because the companions would have been engulfed during the
RGB phase.
\figurename~\ref{fig:todo} hints that there is an apparent dearth of
short-period companions around $\log g \sim 2.5$ (the approximate location of
the red clump).
Another way to look at this is to compare the fraction of subgiant stars with
short-period companions to the same for stars near the \RC.

@@

\subsection{Impossible companions: coherent oscillations?}

@@

\todo{catalogs available online}, full code open source.\footnote{The code used in this
project is available from \url{https://github.com/adrn/TwoFace} under the MIT
open-source software license.}
